---
title: "sellis21_2"
author: "Samantha Ellis"
date: "2024-09-21"
output: html_document
---
 

```{r}
knitr::opts_chunk$set(warning = FALSE, message = FALSE)
dir.create("images")
```

```{r}
install.packages("lpSolveAPI")
```

```{r}
library(lpSolveAPI)
```


In the Weigelt Corporation problem, there are ten decision variables and 12 constraints.The decision variables are the various combinations of Plants (1,2,and 3) and Product Sizes (Large, Medium, and Small).The tenth decision variable that is added for the logistics is "y" for the equal percentage constraint. 

```{r}
#lp object with the 9 decision variables and no constraints
#however, it is entered as 10 decision variables due to the equal percentage constraint later
lprec<-make.lp(0,10)
```

```{r}
#objective function
set.objfn(lprec, c(420,360,300,420,360,300,420,360,300,0))
```

```{r}
#Change lp to max instead of min
lp.control(lprec,sense='max')
```

```{r}
#add constraints

  #Plant 1 Production Capacity 
add.constraint(lprec, c(1,1,1,0,0,0,0,0,0,0), "<=",750)
  #Plant 2 Production Capacity 
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0,0), "<=",900)
  #Plant 3 Production Capacity 
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1,0), "<=",900)

  #Plant 1 Storage Capacity 
add.constraint(lprec, c(20,15,12,0,0,0,0,0,0,0), "<=",13000)
  #Plant 2 Storage Capacity 
add.constraint(lprec, c(0,0,0,20,15,12,0,0,0,0), "<=",12000)
  #Plant 3 Storage Capacity 
add.constraint(lprec, c(0,0,0,0,0,0,20,15,12,0), "<=",5000)

  #Plant 1 Sales 
add.constraint(lprec, c(1,1,1,0,0,0,0,0,0,0), "<=",900)
  #Plant 2 Sales 
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0,0), "<=",1200)
  #Plant 3 Sales 
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1,0), "<=",750)

  #Plant 1 Equal Percentage
add.constraint(lprec, c(1,1,1,0,0,0,0,0,0,-750), "=",0)
  #Plant 2 Equal Percentage
add.constraint(lprec, c(0,0,0,1,1,1,0,0,0,-900), "=",0)
  #Plant 3 Equal Percentage
add.constraint(lprec, c(0,0,0,0,0,0,1,1,1,-450), "=",0)
```

```{r}
write.lp(lprec, filename = "wcp.lp",type = "lp")
```

```{r}
solve(lprec)
```

```{r}
#print model
lprec
```
```{r}
get.objective(lprec)
get.variables(lprec)
```
The maximum profit would be $696,000. 
To approach the maximum profit the variables would need to be the following;
Plant 1
  516 large units produced per day
  177 medium units produced per day
  0 small units produced per day
Plant 2
  0 large units produced per day
  666 medium units produced per day
  166 small units produced per day
Plant 3
  0 large units produced per day
  0 medium units produced per day
  146 small units produced per day
 
Each plant is using 92.6% of its excess capacity. 

